Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-20 main_paper.tex
Change notation for number of bootstraps in bias estimation
I'm letting B_1 represent the number of replications for the bias
correction --- there's no reason to impose that the numbers are
the same.
Add detail to Confidence Interval algorithm
This commit rewrites Algorithm 2 to make the description of the
bootstrap a little more transparent. It also adds a Theorem
stating that the approach is valid. :)

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_B^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta X_i^{*-}))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta X_i^{*+}))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Calculate the bias estimator as
    \begin{equation}
      \label{eq:4}
      \hat\Delta = \tfrac{1}{B} \sum_{k=1}^B \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}

\begin{algorithm}[Confidence intervals]\hfill
 \begin{enumerate}
	\item Obtain bandwidths for both local linear and quadratic regressions $(h_{n}, b_{n})$ using CCT bandwidth choice algorithm procedure.
	\item Estimate local quadratic regression on both sides of cutoff using bandwidth $b_{n}$ from step 1.
	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 2 on each sides of cutoff.
	\item Apply Algorithm~\ref{Alg1} (starting at step 2) to bootstrap data generated in step 3 and obtain bias corrected estimate $\hat{\tau}^{bc*}$.
	\item Repeat step 3 and 4 for $B$ times and obtain confidence interval formed by the $\frac{\alpha}{2}$ and $\left(1-\frac{\alpha}{2}\right)$ percentiles of the empirical distribution of $\hat{\tau}^{bc*}$ .
 \end{enumerate}
\end{algorithm}

>>>>

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
  define
  \begin{align}
    I^-(h) &= \{i : h < X_i < 0\}, &
    I^+(h) &= \{i : 0 < X_i < h\}.
  \end{align}
  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
  $I^-(h_n)$ and $I^+(h_n)$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta X_i^{*-}))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta X_i^{*+}))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Calculate the bias estimator as
    \begin{equation}
      \label{eq:4}
      \hat\Delta = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I^-$, $I^+$, $M^-$, and $M^+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:6}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_2$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_B^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        \label{eq:2}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta X_i^{*-}))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta X_i^{*+}))^2
      \end{align}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
      \end{equation*}
      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\hat\Delta^*$ represent the bias estimate returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimate
      $\hat\mu_+^* - \hat\mu_i^* - \hat\Delta^*$ as $\hat\tau_k^{\prime*}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

Under the same assumptions as earlier, this procedure produces asymptotically
valid confidence intervals.
\begin{theorem}
  Suppose Assumptions~\ref{A1} and~\ref{A3} hold and let $\hat \ell(\alpha)$ and
  $\hat u(\alpha)$ be the interval endpoints produced by Algorithm~\ref{Alg2}
  for some $\alpha \in (0,1)$. Also let $\Pr_\tau$ represent the probability
  distribution of the random variables under the assumption that $\tau$ is
  the true value of the ATE. Then
  \begin{equation}
    \label{eq:5}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau \leq \hat u(\alpha)] \geq 1 - \alpha.
  \end{equation}
  Each of the one-sided intervals is asymptotically valid as well:
  \begin{align}
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\hat\ell(\alpha) \leq \tau ] &\geq 1 - \alpha / 2, &
    \plim_{n \to \infty} \sup_\tau
    \Pr_\tau[\tau \leq \hat u(\alpha)] &\geq 1 - \alpha / 2.
  \end{align}
\end{theorem}
